% This file should be replaced with your file with an appendices (headings below are examples only)

% Placing of table of contents of the memory media here should be consulted with a supervisor
\chapter{Contents of the included storage media}
\dirtree{%
 .1 /.
 .2 LICENSE.
 .2 Makefile.
 .2 requirements.txt.
 .2 README.md.
 .2 thesis.
 .2 thesis.pdf.
 .2 bioblockchain.
 .3 \_\_init\_\_.py.
 .3 bioblockchain.py.
 .3 block.py.
 .3 blockchain.py.
 .3 chain\_utils.py.
 .3 config.py.
 .3 main.py.
 .3 message.py.
 .3 message\_log.py.
 .3 node.py.
 .3 parser.py.
 .3 pbft.py.
 .3 template\_database.py.
 .3 time\_utils.py.
 .3 transaction.py.
 .3 utils.py.
 .3 wallet.py.
 .2 test.
 .2 docs.
 .3 Makefile.
 .3 \_build.
 .4 html.
 .5 index.html.
 .4 pdf.
 .5 bioblockchain.pdf.
 .3 bioblockchain.rst.
 .3 conf.py.
 .3 index.rst.
 .3 make.bat.
 .3 modules.rst.
}

\begin{itemize}
    \item \textbf{thesis} - contains \LaTeX source codes and images needed to compile this text.
    \item \textbf{README.md} - manual for setting up the virtual environment, installing needed packages and running the code.
    \item \textbf{LICENSE} - thesis licensing.
    \item \textbf{Makefile} - makefile containing rules for execution of unit tests, installing packages, cleaning directory and executing the program.
    \item \textbf{bioblockchain} - directory containing all the source codes of implemented demonstrator program.
    \item \textbf{requirements.txt} - description of all the packages needed to execute the program or compile the documentation.
    \item \textbf{test} - directory containing used unit tests (used mainly on cryptographic operations).
    \item \textbf{docs} - directory containing documentation and files with Makefile needed for its compilation.
\end{itemize}
%\chapter{Configuration file}

%\chapter{Scheme of RelaxNG configuration file}

%\chapter{Poster}
